Derogations, Democratic Backsliding, and International Human Rights During the COVID-19 Pandemic

### 2024-12-12 README.qmd
Include other files for readme

---
title: "Derogations, Democratic Backsliding, and International Human Rights During the COVID-19 Pandemic"
format: 
  gfm: 
    wrap: preserve
    toc: true
  typst:
    toc: true
    toc-title: " "
    include-in-header: README_files/better-layout.typ
    author:
    - name: Audrey L. Comstock
      affiliation: Arizona State University
      orcid: 0000-0003-1772-5350
      url: https://audreylcomstock.weebly.com/
      email: audrey.comstock@asu.edu
    - name: Andrew Heiss
      affiliation: Georgia State University
      orcid: 0000-0002-3948-3914
      url: https://www.andrewheiss.com
      email: aheiss@gsu.edu
    - name: Suparna Chaudhry
      affiliation: Lewis and Clark College
      orcid: 0000-0003-3506-7590
      url: https://www.suparnachaudhry.com/
      email: schaudhry@lclark.edu
---

@@

if (knitr::pandoc_to() == "typst") {
  # typst doesn't support emoji as of 0.11.0, so we include SVG versions from 
  # Noto Emoji (https://github.com/googlefonts/noto-emoji) instead
  emoji_out <- "![](README_files/noto-emoji-svgs/emoji_u1f34b.svg){height=1em}![](README_files/noto-emoji-svgs/emoji_u1f608.svg){height=0.8em}"
} else {
  emoji_out <- emoji_glue(":lemon::smiling_face_with_horns:")
}
```

@@

   ![Docker Desktop resource settings](README_files/img/docker-resources.png){width=90%}

@@

     ![Docker Compose contextual menu in the Visual Studio Code sidebar](README_files/img/docker-compose-sidebar.png){width=60%}

>>>>

---
title: "Derogations, Democratic Backsliding, and International Human Rights During the COVID-19 Pandemic"
format: 
  gfm: 
    wrap: preserve
    toc: true
  typst:
    toc: true
    toc-title: " "
    include-in-header: README_stuff/better-layout.typ
    author:
    - name: Audrey L. Comstock
      affiliation: Arizona State University
      orcid: 0000-0003-1772-5350
      url: https://audreylcomstock.weebly.com/
      email: audrey.comstock@asu.edu
    - name: Andrew Heiss
      affiliation: Georgia State University
      orcid: 0000-0002-3948-3914
      url: https://www.andrewheiss.com
      email: aheiss@gsu.edu
    - name: Suparna Chaudhry
      affiliation: Lewis and Clark College
      orcid: 0000-0003-3506-7590
      url: https://www.suparnachaudhry.com/
      email: schaudhry@lclark.edu
---

@@

if (knitr::pandoc_to() == "typst") {
  # typst doesn't support emoji as of 0.11.0, so we include SVG versions from 
  # Noto Emoji (https://github.com/googlefonts/noto-emoji) instead
  emoji_out <- "![](README_stuff/noto-emoji-svgs/emoji_u1f34b.svg){height=1em}![](README_stuff/noto-emoji-svgs/emoji_u1f608.svg){height=0.8em}"
} else {
  emoji_out <- emoji_glue(":lemon::smiling_face_with_horns:")
}
```

@@

   ![Docker Desktop resource settings](README_stuff/img/docker-resources.png){width=90%}

@@

     ![Docker Compose contextual menu in the Visual Studio Code sidebar](README_stuff/img/docker-compose-sidebar.png){width=60%}
